Supplemental Information C: Motives Topic Model

### 2023-06-01 Supplemental Material B - Power Simulation/Supplemental-Material-B-Power-Simulation.tex
si links adj

% Title and header
\title{Supplemental Information A: Annotated Analyses}
\shorttitle{SI A: Annotated Analyses}
%\author{Jannis Kreienkamp, Laura F. Bringmann, Raili F. Engler, Peter de Jonge, Kai Epstude}
\author{[authors masked for peer review]}

@@

This supplementary information documents the methodology and results of all three studies. As part of our open supplemental materials, we share the full RMarkdown file which offers an annotated version of our all analysis steps. This file offers a transparent and reproducible analysis code, which includes full author commentary. We rendered the RMarkdown as an interactive HTML file, which we host as part of our open GitHub repository. We recommend the rendered version for almost all readers (full R code is also available via the rendered version).

\vspace{.5cm}
\begin{tcolorbox}
    \vspace{0.2cm} \centering 
    \href{https://janniscodes.github.io/intergroup-contact-needs/Supplemental-Material-A-Annotated-Analysis}{https://janniscodes.github.io/intergroup-contact-needs/Supplemental-Material-A-Annotated-Analysis}
    \vspace{0.2cm} 
\end{tcolorbox}

>>>>

% Title and header
\title{Supplemental Information B: Power Simulation}
\shorttitle{SI B: Power Simulation}
%\author{Jannis Kreienkamp, Laura F. Bringmann, Raili F. Engler, Peter de Jonge, Kai Epstude}
\author{[authors masked for peer review]}

@@

This supplementary information documents the power simulations we conducted after Study 1. As part of our open supplemental materials, we share the full RMarkdown file which includes transparent and reproducible analysis code. We rendered the RMarkdown as an interactive HTML report, which we host as part of our open GitHub repository. We recommend the rendered version for almost all readers (full R code is also available via the rendered version).

\vspace{.5cm}
\begin{tcolorbox}
    \vspace{0.2cm} \centering 
    \href{https://janniscodes.github.io/intergroup-contact-needs/Supplemental-Material-B-Power-Simulation}{https://janniscodes.github.io/intergroup-contact-needs/Supplemental-Material-B-Power-Simulation}
    \vspace{0.2cm} 
\end{tcolorbox}

### 2023-06-01 Supplemental Material C - Motives Topic Model/Supplemental-Material-C-Topic-Model.tex
si links adj

% Title and header
\title{Supplemental Information A: Annotated Analyses}
\shorttitle{SI A: Annotated Analyses}
%\author{Jannis Kreienkamp, Laura F. Bringmann, Raili F. Engler, Peter de Jonge, Kai Epstude}
\author{[authors masked for peer review]}

@@

This supplementary information documents the methodology and results of all three studies. As part of our open supplemental materials, we share the full RMarkdown file which offers an annotated version of our all analysis steps. This file offers a transparent and reproducible analysis code, which includes full author commentary. We rendered the RMarkdown as an interactive HTML file, which we host as part of our open GitHub repository. We recommend the rendered version for almost all readers (full R code is also available via the rendered version).

\vspace{.5cm}
\begin{tcolorbox}
    \vspace{0.2cm} \centering 
    \href{https://janniscodes.github.io/intergroup-contact-needs/Supplemental-Material-A-Annotated-Analysis}{https://janniscodes.github.io/intergroup-contact-needs/Supplemental-Material-A-Annotated-Analysis}
    \vspace{0.2cm} 
\end{tcolorbox}

For readers interested in the raw files, the raw RMarkdown file is available in our OSF repository \citep[see][]{KreienkampMasked2022a} and can also be accessed as part of the full GitHub repository \citep[][]{KreienkampMasked2022}.

>>>>

% Title and header
\title{Supplemental Information C: Motives Topic Model}
\shorttitle{SI C: Topic Model}
%\author{Jannis Kreienkamp, Laura F. Bringmann, Raili F. Engler, Peter de Jonge, Kai Epstude}
\author{[authors masked for peer review]}

@@

This supplementary information documents the methodology and results of the BERT topic model we conducted as part of embeddedness analyses. To make all supplemental materials as open as possible, we share the full Python Jupyter Notebook file which offers an annotated version of our all analysis steps. This file offers a transparent and reproducible analysis code, which includes full author commentary. An interactive HTML render of the notebook is part of our open GitHub repository. We recommend the rendered version for almost all readers (full Python code is also available via the rendered version).

\vspace{.5cm}
\begin{tcolorbox}
    \vspace{0.2cm} \centering 
    \href{https://janniscodes.github.io/bert-migrant-need-content/Supplemental-Material-C-BERT-topic-model-outgroup}{https://janniscodes.github.io/bert-migrant-need-content/Supplemental-Material-C-BERT-topic-model-outgroup}
    \vspace{0.2cm} 
\end{tcolorbox}

For readers interested in the raw files, the raw Jupyter notebook is available in our OSF repository \citep[see][]{KreienkampMasked2022a} and can also be accessed as part of the full GitHub repository \citep[][]{KreienkampMasked2022}. Please note that this analysis used free text responses from our participants. To protect the privacy and confidentiality of our participants, we do not make the raw data openly accessible. If you would like to request access to the raw data, please reach out to the corresponding author.
